Verifying Demonstrations

### 2018-08-29 paper/protocol.tex
Edits protocol: fixes lots of typos

\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).

\emph{Registration: \(\sk\gets 
    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{CA}][\ssk]}\).}
During the registration phase, each protester generates a secret key and obtains a signature on it by the \ac{CA} but without revealing it to the \ac{CA}.
At the end, each protester will have a signed secret key while the \ac{CA} will issue only one signature per protester but without knowing the association between a particular key and the identity of the user.
The protester chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x M^{axy})\) and sends it to the protester.
The protester then verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the protester sets \(\sk = (\sigma, k, r)\).

@@

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the participant and the witness construct the proof share of the participant (\cref{fig:ProofFig}).
The participant blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The participant sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the participant as the prover and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows\footnote{Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple times to achieve security.}.
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the participant computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the participant.
As a consequence, both the participant and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the participant (\cref{fig:ProofFig}).

@@

\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is only for redundancy.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[ \psh_W = (\cid, \pid, \wid, t_s, 
  t_s', t_e', l, \pi_{\wid}) \] for permanent storage.

@@

While there are various ways for verifying the participation count, hereafter we will detail the two suggested just after \cref{DefParticipationCount}.
In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
In the second approach, we have a higher trust in specific witnesses and no 
trust in others.
In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.

To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   
  (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
    (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify 
\(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the 
latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of 
\(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq  
  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.
It is the strength function \(\str\) that differ in the two cases we give.

In the case \emph{without} trusted witnesses, the verifier simply define 
\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to our 
desired thresold.

In the case \emph{with} trusted witnesses, each trusted witness must inform the 
verifier of which proof shares that he or she has signed, \eg by giving a list 
of all such proof shares or digitally sign each proof share.
Then the verifier defines \[
  \str[\prf_{\pid_i, P}] = \begin{cases}
    1 & \text{if \(\prf_{\pid_i, P}\) is such a proof share} \\
    0 & \text{otherwise}
  \end{cases}
\] and sets \(\theta = 1\).

>>>>

\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).

\emph{Registration: \(\sk\gets 
    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
The participant acts as prover and the \ac{CA} as verifier while they perform 
the following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
  C = A^x M^{axy})\) and sends it to the participant.
The participant then verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the participant and the witness construct the proof share of the participant (\cref{fig:ProofFig}).
The participant blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The participant sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the participant as the prover and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k_P+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple 
times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the participant computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\pi = 
  (\pid, \wid, t_s, t_s', l)\), which forms a proof share for the protester 
(\cref{fig:ProofFig}).

@@

\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[ \psh_W = (\cid, \pid, \wid, t_s, 
  t_s', t_e', l, \pi_{\wid}) \] for permanent storage.

@@

While there are various ways for verifying the participation count, hereafter, 
we will detail the two suggested just after \cref{DefParticipationCount}.
In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
In the second approach, we trust specific witnesses, but no others.
In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
It is the strength function \(\str\) of \cref{DefParticipationCount} that 
differ in the two cases.
We will first give the procedure and then how to construct the two different 
strength functions.

To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   
  (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
    (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})\) for each protester \(j\) 
from the blockchain, verify \(\prf_{\pid_j}^{(i)}\), \(\prf_{\wid_i}\) and that 
the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime (i)})}{\min(t_e^{(i)}, 
    t_e^{\prime (i)})}\) is a subset of \(t\) and that \(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

In the case \emph{without} trusted witnesses, the verifier simply define 
\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to the 
desired threshold.

In the case \emph{with} trusted witnesses, each trusted witness must inform the 
verifier of which proof shares that he or she has signed, \eg by giving a list 
of all such proof shares or digitally sign each proof share.
Then the verifier can define \[
  \str[\prf_{\pid_i, P}] = \begin{cases}
    1 & \text{if \(\prf_{\pid_i, P}\) is such a proof share} \\
    0 & \text{otherwise}
  \end{cases}
\] and sets \(\theta = 1\).
